### 2024-08-08 paper-reviews/papers-2024.tex
Fix latex build
Add dropout paper

    FlashFFTConv algorithm proposed in the paper tries to address major bottlenecks related to convolutional models with long filters --- poor utilization of specialized matrix multiplication units and expensive I/O between layers of memory hierarchy. The major bottleneck is caused by the Fast Fourier Transform. Convolutional models lag behind the most Transformers even though FFT allows to run in O(N log N) instead of  O(N^2) common Transformers. FlashFFTConv uses a matrix decomposition that computes FFT using matrix multiplication units and enables kernel fusion for long sequences that in turn allows to reduce the expensive I/O operations.

@@

    The paper presents an improved version of Flash Attention algorithm. The main change include: 1. reduced number of non-matmul FLOPs (matmul throughput can be up to 16X higher than non-matmul throughput); 2. parallelization along sequence length dimension in both forward and backward passes; 3. work partitioning aimed to reduce communication and shared memory accesses. FlashAttentionV2 is claimed to be around 2X faster than FlashAttention.
\end{itemize}

>>>>

    FlashFFTConv algorithm proposed in the paper tries to address major bottlenecks related to convolutional models with long filters --- poor utilization of specialized matrix multiplication units and expensive I/O between layers of memory hierarchy. The major bottleneck is caused by the Fast Fourier Transform. Convolutional models lag behind the most Transformers even though FFT allows to run in $O(N log N)$ instead of  $O(N^2)$ common Transformers. FlashFFTConv uses a matrix decomposition that computes FFT using matrix multiplication units and enables kernel fusion for long sequences that in turn allows to reduce the expensive I/O operations.

@@

    The paper presents an improved version of Flash Attention algorithm. The main change include: 1. reduced number of non-matmul FLOPs (matmul throughput can be up to 16X higher than non-matmul throughput); 2. parallelization along sequence length dimension in both forward and backward passes; 3. work partitioning aimed to reduce communication and shared memory accesses. FlashAttentionV2 is claimed to be around 2X faster than FlashAttention.

    \item \cite{Hinton:Dropout:2012}:

    The paper described dropout training approach aimed to prevent co-adaptation between several feature detectors within a network. The co-adaptation often leads to overfitting of the network. This problem is greatly reduced by randomly omitting results of some (half in the paper) feature detectors. The dropout ensures that each neuron learns to detect a feature in isolation that is in turn improves network's performance as demonstrated by the paper.
\end{itemize}
